Supplementary Information

### 2020-11-30 doc/manuscript/MEE_manuscript.Rmd
small update

To test for $DBH \times$ climate interactions and $year$ effects, we limited the analysis of each species to years for which the $DBH$ range represented by at least 3 individuals spanned at least half the total range of that species, dropping species entirely if < 30 years met this criteria.  **(HAVE YET TO TRY THIS) **
For models including interactive effects of climate and $DBH$, we tested for interactions between first-order linear terms for climate variables and $DBH$.
For models including $year$, we tested for first-order linear effects of $year$.
To verify that GLS model trends for $year$ were real, as opposed to an artifact of inherent covariation between $DBH$ and $year$ within each core, we separately analyzed $DBH$-growth relationships by decade (Appendix `r decadal_analysis_appendix`). **(CAMERON'S WORK [IN THIS REPO](https://github.com/EcoClimLab/tree-rings_global-change))**
For simplicity and consistency with previous literature, we present only the models with $BAI$ as the growth metric, noting that responses were similar across metrics.

>>>>

To test for $DBH \times$ climate interactions and $year$ effects, we limited the analysis of each species to years for which the $DBH$ range represented by at least 3 individuals spanned at least half the total range of that species, dropping species entirely if < 30 years met this criteria.  **(HAVE YET TO TRY THIS) **
For models including interactive effects of climate and $DBH$, we tested for interactions between first-order linear terms for climate variables and $DBH$.
For models including $year$, we tested for first-order linear effects of $year$.
To verify that GLS model trends for $year$ were real, as opposed to an artifact of inherent covariation between $DBH$ and $year$ within each core, we separately analyzed $DBH$-growth relationships by decade (Appendix `r decadal_analysis_appendix`). 
For simplicity and consistency with previous literature, we present only the models with $BAI$ as the growth metric, noting that responses were similar across metrics.
